On the Functionality of the Multilayer Perceptron

### 2020-11-22 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Progress on draft, Added new figures, removed old figures

\paragraph*{}The application of neural networks to image-processing and recognition has been well studied and developed in the last few decades \cite{Geron,Goodfellow,Loy,Mierswa}. As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior. Following this success, it make senses to provide an image-like representation of a sound wave as a feature. We do this in the form of a \textit{spectrogram} matrix. A spectrogram is a representation of the energy distribution of a sound wave as a function of both frequency and time. In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis. Thus each point in the 2-Dimensional space is an energy at a given time and frequency. Examples spectrograms from the wave form data set are shown in Fig. (\ref{fig-spectrograms}).
\begin{figure}[H]
\begin{center}
\textcolor{red}{Insert spectrograms here}
\caption{Spectrogram representations of various waveforms}
\label{fig-spectrograms}
\end{center}
\end{figure}

@@

\paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame. A standard \textit{Hanning Window} of $N$ samples is generated as a $1 \times N$ row-array, $H$. The $n$-th index in a Hanning window with $N$ samples is defined:
\begin{equation}
\label{eqn-Hanning}
H[n] = \frac{1}{2}\bigg[ 1 - \cos\Big( \frac{2\pi n}{N-1}\Big)\bigg]
\end{equation}
This window function is applied to each analysis frame by computing the element-wise product of the Hanning window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$. The result is another $k \times N$ array, $\widetilde{A}$:
\begin{equation}
\label{eqn-WindowMatrix}
\widetilde{A_i} = A_i \odot H
\end{equation}
We show the effect of a Hanning window on a wae 
\begin{figure}[H]

	\begin{subfigure}{1.0\textwidth}
	\centering
	%\includegraphics[width=\textwidth , height=0.2\textheight]{../FiguresFeatures/Auto_Correlation_4}
	\caption{A section of a waveform, $1024$ samples long}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	%\includegraphics[width=\textwidth , height=0.2\textheight]{../FiguresFeatures/Auto_Correlation_4}
	\caption{The Same waveform with a Hanning Window Applied}
	\end{subfigure}

>>>>

\paragraph*{}The application of neural networks to image-processing and recognition has been well studied and developed in the last few decades \cite{Geron,Goodfellow,Loy,Mierswa}. As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior. Following this success, it make senses to provide an image-like representation of a sound wave as a feature. We do this in the form of a \textit{spectrogram} matrix. A spectrogram is a representation of the energy distribution of a sound wave as a function of both frequency and time. In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis. Thus each point in the 2-Dimensional space is an energy at a given time and frequency. Examples spectrograms from the wave form data set are shown in Fig. (\ref{fig-spectrograms}).
\begin{figure}[H]
\begin{center}
\textcolor{red}{Insert spectrograms here}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=0.45\textwidth , height=0.2\textheight]{../Figures/AnalysisFrame}
	\caption{A section of a violin bowing an $A4$ note, $1024$ samples long}
	\end{subfigure}
\caption{Spectrogram representations of various waveforms}
\label{fig-spectrograms}
\end{center}
\end{figure}

@@

\paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame. A standard \textit{Hanning Window} of $N$ samples is generated as a $1 \times N$ row-array, $H$. The $n$-th index in a Hanning window with $N$ samples is defined:
\begin{equation}
\label{eqn-Hanning}
H[n] = \frac{1}{2}\bigg[ 1 - \cos\Big( \frac{2\pi n}{N-1}\Big)\bigg]
\end{equation}
This window function is applied to each analysis frame by computing the element-wise product of the Hanning window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$. The result is another $k \times N$ array, $\widetilde{A}$:
\begin{equation}
\label{eqn-WindowMatrix}
\widetilde{A_i} = A_i \odot H
\end{equation}
We show the effect of a Hanning window on an analysis frame:
\begin{figure}[H]

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]{../Figures/AnalysisFrame}
	\caption{A section of a violin bowing an $A4$ note, $1024$ samples long}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]{../Figures/WindowedFrame}
	\caption{The same waveform with a Hanning Window Applied}
	\end{subfigure}
